Supplement to: Learning Libraries of Subroutines for Neurally--Guided Bayesian Program Learning

### 2018-05-17 supplement.tex
First geom addition to supplement

>>>>

\section{Learning abstract geometry}
The brifly presented geometry project is a recent addition to the set of
problems adressed with our method. The original DSL, while inspired by the
Logo~\cite{abelson1974logo} in the sense that ones controls a moving on-off
point, was designed to be congitively plausible in the sense that some
abstractions are baked in for curves and a few structures --- it was first
described in~\cite{sablemeyer2017geom}.

It is to be thought as a turtle with as internal state a position, a facing
direction, a speed, an acceleration, an angular speed and an angular
acceleration.

The DSL is the following:

\begin{center}
\tt
\begin{tabular}{rr}
  \toprule
  \textrm{\emph{name}}    & \textrm{\emph{type}} \\
  \midrule
  Concat    & \text{prog}      \to \text{prog}      \to \text{prog} \\
  Repeat    & var option        \to \text{prog}      \to \text{prog} \\
  Embed     & \text{prog}      \to \text{prog}                       \\
  Define    & \text{var}        \to \text{prog}                       \\
  Turn      & \text{var option} \to \text{prog}                       \\
  Integrate & \text{var option} \to \text{bool}       \to              \\
            & \text{var option} \to \text{var option} \to              \\
            & \text{prog}                                             \\
  \midrule
  True      & bool                                                     \\
  False     & bool                                                     \\
  \midrule
  Nothing   & \text{var option}                                        \\
  Just      & \text{var}        \to \text{var option}                  \\
  \midrule
  Unit      & var                                                      \\
  Name      & var                                                      \\
  Next      & \text{var}        \to \text{var}                         \\
  Prev      & \text{var}        \to \text{var}                         \\
  Double    & \text{var}        \to \text{var}                         \\
  Half      & \text{var}        \to \text{var}                         \\
  Opposite  & \text{var}        \to \text{var}                         \\
  \bottomrule
\end{tabular}
\end{center}

In this context programs to be learned are directly resulting shapes, since they
don't take an input, and all tasks will be unique in the sense that each program
ignores input and produces a single output.

Some elements of the semantics are common, the others are as follow.
\texttt{Repeat} takes a \texttt{variable} and a \texttt{prog} and repeats
said \texttt{prog} $n$ times where $n$ is the evaluation of the
\texttt{variable} --- if not set it is defaulted to two. \texttt{Embed} of a
\texttt{prog} means that said \texttt{prog} will be executed and then returns to
the current state --- leaving what has been drawn in the meantime on the canvas.
\texttt{Integrate} is the main instruction and the only one that draws anything:
\texttt{Integrate(t,p,a,c)} takes a time \texttt{var}, a pen \texttt{bool}, an
acceleration \texttt{var} and an angular speed \texttt{var}, and it moves the
turtle according to these parameters --- with or without actually drawing
depending on the pen variable \texttt{p}.

\begin{wrapfigure}{r}{0.25\textwidth}
  \begin{center}
    \includegraphics[width = 0.25\textwidth]{figures/DSLGeom.eps}
  \end{center}\label{dslgeom}\caption{Some defaults for \texttt{Integrate}}
\end{wrapfigure}

The default values of these parameters are set such that \texttt{Integrate(nothing,
true, nothing, nothing)} draws a unit segment, \texttt{Integrate(nothing, true,
nothing, Just(Unit))} draws a circle of unit length, and
\texttt{Integrate(nothing, true, Just(Unit), Just(unit))} draws the first spire
of a spiral.

The training was done on the following set of tasks

\begin{figure}[h]
\centering
\includegraphics[width = \textwidth]{figures/geomAllTasks.png}
  \caption{The set of tasks for the geometry domain}
\end{figure}
